\chapter*[Introduction]{Introduction}
\addcontentsline{toc}{chapter}{Introduction}

The Climate Change is on of the main study fields over the last decades; causing great concern both within and outside the scientific community. It was first discovered the relationship between burning fossil fuel that increases the Greenhouse Effect, this process was called Global Warming. However, it was later discovered that the planet was not warming in a uniform manner. Sometimes with even with colder winters in some regions. For this reason, this phenomena was renamed to \textit{Climate Change} or \textit{Climate Crisis}.

The disparity between climate scientists' predictions and reality has been noticed by society over the past few years. This generates social anxiety and paralysis, as we do not know the best route to solve the problem. Weather forecasts' uncertainty hinders agriculture and other sectors of the economy. The Climate Change has also already caused deaths and put lives at risk due to problems such as floods, inundations, droughts, and other catastrophic events.

This thesis aims to provide a better understanding of the thermodynamics of Earth's atmosphere, as well as to suggest technologies to stabilize the climate and mitigate possible future extreme weather events. Initially, the focus is on understanding the mistaken attribution of fossil fuel combustion as the main driver of the climate catastrophes occurring around the world. Next, tools will be presented to eliminate extreme weather events and, consequently, achieve greater climate stability. Finally, possible future work and areas of study will be presented to deepen the understanding of global climate functioning.